---
title: "Portfolio Summary"
author: "Gryffindor"
date: "12/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Risk Classification

The risk simulation is based on research on the benefit of repeated sampling in understanding risk conducted by the University of Mannheim. See <http://simulator.behavioral-finance.de/#!/> for further information. The portfolio is constructed according to the risk assessment conducted in the beginning of the App, where each risk class corresponds to a yearly standard deviation as a proxy for risk.


## Investment Universe

The portfolio has been constructed in accordance with the country and industry preferences specified. Geographically, your portfolio includes securities listed in the following countries: `r input$mymap_groups`. The industries that have been chosen to exclude are: `r input$industry1`.

To sum up, the portfolio has been constructed based on the following ETFs: `r colnames(newData())`.


## Portfolio Composition

The portfolio has been constructed in accordance with the country and industry preferences specified. The portfolio consists of ...


```{r echo=FALSE, fig.height=5, fig.width=5, fig.align='center'}
piechart()
```


## Performance Chart

Considerations about the performance...
```{r echo=FALSE, fig.align='center'}
randperform()
```

```{r echo=FALSE, fig.align='center'}
testplot(newData())
```


## Max Drawdown


