---
title: "Portfolio Summary"
author: "Gryffindor"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Risk Classification

The risk simulation is based on research on the benefit of repeated sampling in understanding risk conducted by the University of Mannheim. See <http://simulator.behavioral-finance.de/#!/> for further information. The portfolio is constructed according to the risk assessment conducted in the beginning of the App, where each risk class corresponds to a yearly standard deviation as a proxy for risk.


## Investment Universe

The portfolio has been constructed in accordance with the country and industry preferences specified. Geographically, your portfolio includes securities listed in the following countries: `r input$mymap_groups`. The industries that have been chosen to exclude are:
```{r echo=FALSE, results='asis'}
if (("NorthAmerica" %in% input$mymap_groups) || ("Asia" %in% input$mymap_groups) || ("Europe" %in% input$mymap_groups)) {
    if (is.null(input$industry1)) {
        cat("You invest in all industrie")
    } else {
        cat(input$industry1, sep = ", ")
    }
} else {
    cat("TestTestTest")
}
```


To sum up, the portfolio has been constructed based on the following ETFs: `r colnames(newData())`.


## Portfolio Composition

The portfolio has been constructed in accordance with the country and industry preferences specified. The portfolio consists of ...


## Your Perforance

```{r echo = FALSE, results = 'asis'}
if(input$rpref2 == 1 && input$inv_horizon <= 5){
      plot.ts(shortbond)
      summary(shortbond)
}

if((input$rpref2 == 2 && input$inv_horizon <= 5) ||
   (input$rpref2 == 1 && input$inv_horizon > 5 && input$inv_horizon <= 10)){
      plot.ts(longbond)
      summary(longbond)
}

if(input$rpref2 == 1 && input$inv_horizon <= 5){
      plot.ts(shortbond)
      summary(shortbond)
}
```


## Max Drawdown


